Output Summary

### 2022-01-11 03-post-process/compare-sim-to-obs.Rmd

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
output: html_document
params:
  scenario:
    label: "Scenario"
    value: "new-BH"
    input: text
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
output: html_document
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---

### 2022-01-11 03-post-process/output-plots.Rmd

# extract the two key structures from this object
# post = model_info$post
post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data
```

>>>>

# extract the two key structures from this object
post = model_info$post
# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data
```
